\documentclass[12pt,oneside]{report}

% ---------- Packages ----------
\usepackage[a4paper,margin=1in]{geometry}
\usepackage{lmodern}
\usepackage[T1]{fontenc}
\usepackage{setspace}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{array}
\usepackage{fancyhdr}
\usepackage{tcolorbox}
\usepackage{listings}
\usepackage{tikz}
\usetikzlibrary{arrows.meta, positioning, shapes, fit}

% ---------- Colors & links ----------
\definecolor{ABSEBlue}{HTML}{0F6FC6}
\definecolor{ABSEGray}{HTML}{4D5866}
\hypersetup{
  colorlinks=true,
  linkcolor=ABSEBlue,
  urlcolor=ABSEBlue,
  citecolor=ABSEBlue
}

% ---------- Header / Footer ----------
\pagestyle{fancy}
\fancyhf{}
\lhead{\textit{Multi-Agent Daily Planning System (MADPS)}}
\rhead{\thepage}
\renewcommand{\headrulewidth}{0.4pt}

% ---------- Title Format ----------
\titleformat{\chapter}{\Large\bfseries\color{ABSEBlue}}{\thechapter.}{0.5em}{}
\titleformat{\section}{\large\bfseries\color{ABSEGray}}{\thesection}{0.5em}{}

% ---------- Code style ----------
\lstdefinestyle{code}{
  basicstyle=\ttfamily\small,
  frame=single,
  breaklines=true,
  columns=fullflexible
}

% ---------- Title ----------
\begin{document}
\begin{titlepage}
  \centering
  {\Large \textbf{SENG 696 — Agent-Based Software Engineering}\par}
  \vspace{1.5cm}
  {\huge \textbf{Multi-Agent Daily Planning System (MADPS)}\par}
  \vspace{1.3cm}
  {\Large \textbf{Report 1A}\par}
  {\Large \textbf{System Specification}\par}
  \vspace{1.2cm}
  {\large Ali Mohammadi Ruzbahani [30261140], Shuvam Agarwala [30290444]\par}
  \vspace{1.2cm}
  {\large \textbf{Course} \par}
  {\large \textbf{Agent-Based Software Engineering (SENG 696)} \par}
  \vspace{1.2cm}
  {\large \textbf{Instructor:} Professor Behrouz Far\par}
   \vspace{2.2cm}

  {\large \textbf{Date:} \today\par}
  \vfill

\end{titlepage}

\tableofcontents
\onehalfspacing
\clearpage

% =====================================
% 1A. System Specification (Short Doc)
% =====================================
\chapter*{1A. System Specification}
\addcontentsline{toc}{chapter}{1A. System Specification}

\section{Overview}
\textbf{System Name:} MADPS — Multi-Agent Daily Planning System.\\
\textbf{Primary Users:} Individuals (students/professionals) planning their daily schedule.\\
\textbf{Context:} Web/desktop UI with local agent processes.

\section{Scope \& Functionalities}
\begin{itemize}[leftmargin=1.2cm]
  \item \textbf{Task Intake \& Management:} Create/edit tasks, deadlines, dependencies, effort estimates, tags.
  \item \textbf{User Modeling:} Learn energy/productivity patterns from completion history and feedback.
  \item \textbf{Planning \& Adaptation:} Generate daily schedule; re-plan quickly after disruptions (overruns/new tasks).
  \item \textbf{Priority Policy:} Combine deadlines, importance, and learned preferences.
  \item \textbf{Visualization \& Control:} Calendar-style view; drag-and-drop with immediate reconciliation.
  \item \textbf{Notifications:} Start/stop nudges, conflict alerts, buffer warnings.
  \item \textbf{Storage:} Local DB (SQLite/PostgreSQL) with export to JSON/CSV.
\end{itemize}

\section{Constraints, Assumptions, Non-Goals}
\textbf{Constraints:} No external context integrations (weather/traffic). Single-user setup. Re-planning latency $\leq$ 1.5s for typical day ($\leq$ 40 tasks).\\
\textbf{Assumptions:} User supplies core task metadata. Energy model starts generic, personalizes over time.\\
\textbf{Non-Goals:} Cross-user coordination, resource booking, travel routing, mood detection.

\section{Success Metrics}
\begin{itemize}[leftmargin=1.2cm]
  \item $\geq$ 25\% fewer deadline violations vs. rule-based baseline.
  \item $\geq$ 20\% improvement in on-time task starts.
  \item User satisfaction $\geq$ 4/5 after 7 days.
\end{itemize}

\clearpage
\end{document}